Study protocol

### 2021-09-08 Manuscript/S1.Protocol.Rmd
white space cleaning
added page break after TOC
add reminder to put some more info in S1
add pdf output

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  github_document:
    toc: yes
---

@@

@@

The process of predicting labels and manually reviewing them is what defines a "classification and review (CR) iteration".

>>>>

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  pdf_document:
    toc: yes
  github_document:
    toc: yes
---

\newpage

@@

Add intallation and setup info here

@@

The process of predicting labels and manually reviewing them is what defines a "classification-review (CR) iteration".
